Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-02-02 documents/ms.tex
fixing #5

To sample the posterior in a way that is sensitive to potential multimodality,
we use the \texttt{emcee3} MCMC sampler.
We initialize 500 walkers with random samples from the prior and use a mix of
different proposal distributions: specifically, a 2:2:1 mix of KDE,
differential evolution, and DESnooker moves.
[DFM: more words/citations here?]
We run fifty steps of the sampler at a time, checking for convergence after
each iteration, up to a maximum of fifty iterations.
We declare convergence if the total effective chain length is at least
8$\times$ the maximum autocorrelation time.
When convergence is achieved, we drop the first two autocorrelation lengths in
the chain as a burn-in, and randomly choose 5000 samples as representative of
the posterior.
This fitting process takes several hours for a typical simulated light curve,
though in some cases it can take 12 hours or longer to converge.

>>>>

To sample the posterior in a way that is sensitive to potential multimodality,
we use the \texttt{emcee3}\footnote{\url{https://github.com/dfm/emcee3}} MCMC
sampler.
\texttt{emcee3} is the successor to the \texttt{emcee} project
\citep{Foreman-Mackey2013} that includes a suite of ensemble MCMC proposals
that can be combined to efficiently sample more distributions than the stretch
move \citep{Goodman2010} in \texttt{emcee}.
For this project, we use a weighted mixture of three proposals.
First, we include a proposal based on the \texttt{kombine}
package\footnote{\url{https://github.com/bfarr/kombine}} (Farr \& Farr, in
prep.) where a kernel density estimate (KDE) of the density represented by the
complementary ensemble is used as the proposal for the other walkers.
The other two proposals are a ``Differential Evolution (DE) MCMC'' proposal
\citep{terBraak2006, Nelson2014} and the ``snooker'' extension of DE
\citep{terBraak2008}.

We initialize 500 walkers with random samples from the prior and use a
weighted mixture of the KDE, DE, and snooker proposals with weights of 0.4,
0.4, and 0.2 respectively.
We run fifty steps of the sampler at a time, checking for convergence after
each iteration, up to a maximum of fifty iterations.
We declare convergence if the total effective chain length is at least
8$\times$ the maximum autocorrelation time.
When convergence is achieved, we drop the first two autocorrelation lengths in
the chain as a burn-in, and randomly choose 5000 samples as representative of
the posterior.
This fitting process takes several hours for a typical simulated light curve,
though in some cases it can take 12 hours or longer to converge.
